Homework

### 2016-06-30 Macro Impacts.tex
We need to solve for A_i in terms of Sigma_i
This shouldn’t be hard. It’ll just take some playing around with the
equations.
For shocks, check the laser physics book
Corrected Things

which are non-singular. They yield

@@

This reveals two facts. The first fact is that the only relevant equations are 34-36. The second is that 37 implies that
0&=k^2\ps{\f{\Sigma_{yz}}{k_yk_z}+\f{\Sigma_{zx}}{k_zk_x}+\f{\Sigma_{xy}}{k_xk_y}}\,.

>>>>

which is non-singular. They yield

@@

This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations. In other words, we have shown that you can always diagonalize the stress tensor.
We now solve for $A_i$ in terms of $\Sigma_i$.
We still have a gauge degree of freedom...
For shocks, check the laser physics book.
